%\titleformat{\section}
 % {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\section*{Acknowledgments}

I am grateful to my advisor, Dr. Reza Zafarani of the Department of EECS at
Syracuse University. He guided me throughout my research and helped me overcome various obstacles that I faced. Dr. Zafarani directed me in the right path during my research and advised of various prospective areas to explore. Along with Dr. Zafarani, Dr. Russo helped me understand the psychological aspects of my research. I am thankful to them for the encouragement and constant support.

I would also like to thank the experts who were involved in the Defense Committee without whose participation,  the Defense could not have been successfully conducted:
\begin{itemize}
\item Dr. Natalie Russo, Assistant Professor, Department of Psychology
\item Dr. Senem Velipasalar Gursoy, Associate Professor, Department of Electrical Engineering and Computer Science
\item Dr. Edmund Yu, Associate Professor, Department of Electrical Engineering and Computer Science
\end{itemize}

I would like to give credit to my parents Mamatha and Gowri Shankar Sambatur, my brother Abhishek Shankar for always motivating me. Also, I would like to thank my friends Sai Venkat Kotha, Ayesha Ahmad and Rashmi K. Shivanna, who supported and rooted for me during this journey. Finally, I am also grateful to my laboratory mates who assessed and advised on various aspects of my thesis. This accomplishment would not have been possible without all these people. 

\hfill\emph{Sambatur, Siri Chandana}\\
\hspace*{0pt}\hfill\emph{Syracuse, New York}\\
\hspace*{0pt}\hfill\emph{May, 2018}
